2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Draft data set complete

# Draft Prep
Armed with this information, here's what I need before the draft:

1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
2. Add pitchers to the above plot so that I can...
3. ...put together a basic plan of attack for the draft
4. Generate a cheat sheet document to use for the draft

@@

*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*

I'd like to put together a plan of attack where, for each round, I identify the kinds of players available at the highest projected scoring, perhaps in tiers of z_scores: >= 15, 10-15, 5-10, etc. Let's start with the upper tier:

##### Elite Tier (z_score >= 15)

```{r echo = FALSE}
positions_ranked_with_keepers %>%
  filter(z_sum >= 15) %>%
  select(Name, z_sum, ADP, round) %>%
  unique() %>%
  arrange(ADP) %>%
  kable()
```

We should assume Trout, Betts, and Ramirez will go 1,2,3, or at least not make it to me at 11. However, according to the projection data, Bryce Harper & Juan Soto could be available, potentially worth getting at the rounds 1 & 2 turn.

>>>>

# Draft Prep
The above plot is reproduced below to exclude known keepers and include pitchers.

@@

Below is a plot of z_score by round so I can identify in which rounds to target specific positions, particularly once we pass to below a z_score of 10. 
```{r echo=FALSE}
positions_ranked_with_keepers %>%
  filter(!keeper,
         ADP <=300) %>%
  group_by(round, position) %>%
  summarize(low = min(z_sum),
            mid = median(z_sum),
            high = max(z_sum),
            n = n()) %>%
  arrange(round) %>%
  ggplot(aes(y=mid, x=round, color=n)) +
  geom_pointrange(aes(ymax = high,ymin = low)) +
  labs(x="Round (ADP)", 
        y="Z_Score") +
  facet_wrap(~ position) -> rv

ggplotly(rv)
```
*Note, one of the excluded keepers is mine - SS Trevor Story, round 11*

Here's the data set with which I'll print a little cheat sheet (or interactive app?) for the draft.

```{r echo=FALSE}
batters_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions) -> batters_draft

batters_draft %>%
  mutate(rn = row_number()) %>% 
  filter(grepl("Robertson",Name)) %>%
  select(rn) %>%
  pull() -> robertson_drop

batters_draft %>%
  mutate(rn = row_number()) %>% 
  filter(grepl("Jose Ramirez",Name)) %>%
  select(rn) %>%
  pull() -> jramirez_drop

rows_drop <- c(robertson_drop[-1],jramirez_drop[-1])

batters_draft %>%
  slice(-rows_drop) -> batters_draft

pitchers_ranked %>%
  select(Name, z_rank, z_sum, ADP, positions) -> pitchers_draft

pitchers_draft %>%
  mutate(rn = row_number()) %>%
  filter(grepl("Cody Reed",Name)) %>%
  select(rn) %>%
  pull() -> reed_drop

pitchers_draft %>%
  mutate(rn = row_number()) %>%
  filter(grepl("Will Smith",Name)) %>%
  select(rn) %>%
  pull() -> smith_drop

rows_drop <- c(smith_drop[-1], reed_drop[-2])

pitchers_draft %>%
  slice(-rows_drop) -> pitchers_draft

rm(rows_drop, robertson_drop, jramirez_drop, reed_drop, smith_drop)

pitchers_draft %>%
  bind_rows(batters_draft) %>%
  mutate(round = ceiling(ADP/12)) %>%
  select(z_rank, Name, z_sum, round, ADP, positions) %>%
  arrange(z_rank) -> draft_df

draft_df %>% saveRDS("data/draft_dataset.Rds")

draft_df %>%
  head(25) %>%
  kable()
```
